Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-14 paper.tex
Discuss profiles a bit

Mean velocity profiles at one turbine diameter downstream are shown in
Figure~\ref{fig:profiles}. The 2-D results suffer from a blockage
mismatch, i.e. keeping the proximity of the walls constant increases the
blockage ratio.

@@

>>>>

Mean velocity profiles at one turbine diameter downstream are shown in
Figure~\ref{fig:profiles}. The 2-D results suffer from a blockage mismatch, i.e.
keeping the proximity of the walls constant increases the blockage ratio. The
3-D results, however, show good agreement with the experiments.

@@

Both Spalart--Allmaras cases do a poor job predicting the turbulence kinetic
energy in the flow, since it must be resolved as variance in the velocity field.
The 2-D SST model does a good job predicting the peak in $k$ at $y/R=-1$, though
is missing the smaller peak at $y/R=-1$. This is once again likely due to
blockage issues, where local tip speed ratio is decreased, increasing the
blades' instantaneous angle of attack at this location on the downstream
passage. In contrast, the 3-D SST model predicts the $+y$ peak in turbulence
kinetic energy very well, though the $-y$ peak magnitude is overpredicted by
about 30\%. We also see some smearing of $k$ across the center of the rotor,
which is likely due to exaggerated levels of the turbulent eddy viscosity.
